Multisensor Architecture for an Intersection Management System

### 2015-06-11 ch4-laser.tex
Initiated chapter 4

\section{Preprocessing and Background removal}
\section{Object Recognition}
\section{Feature Extraction}
\section{Tracking and Classification}

>>>>

In this chapter is described the development of a laser based system for intersection monitoring

\section{Preprocessing and Background removal}

The first step in processing laser data is the removal of irrelevant frames, maybe due to communication errors or due to corrupted data. For this stage is proposed a filter based on the of entropy of data, calculated for each frame.

\section{Object Recognition}
\section{Feature Extraction}
\section{Tracking and Classification}
